plots with prolactin

### 2020-02-04 analysis/07_hormones.Rmd
new images

write.csv(table1, "../../parentalhormones/data/table-1.csv")
write.csv(table2, "../../parentalhormones/data/table-2.csv")

@@

>>>>

@@

## summary for owen

```{r}
meanTE <- hormoneswide %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(meanTestosterone = (mean(testosterone, na.rm = TRUE)), 
                   meanEstradiol = mean(estradiol, na.rm = TRUE)) %>%
  dplyr::mutate(meanTestosterone = round(meanTestosterone,2)) %>%
  dplyr::mutate(meanEstradiol = round(meanEstradiol,2)) %>%
  dplyr::filter(treatment %in% charlevels) %>%
  droplevels() %>%
  dplyr::mutate(timepoint = as.numeric(treatment)) %>%
  select(timepoint, treatment, meanTestosterone, meanEstradiol)
meanTE
```

```{r savefiles}
write.csv(meanTE, "../results/07_meanTE.csv", row.names = F)
write.csv(hormones, "../results/07_hormones.csv", row.names = F)
write.csv(hormoneswide, "../results/07_hormoneswide.csv", row.names = F)
```

### 2020-02-04 analysis/16_PRL.Rmd
new images

candidategenes <- c("PRL", "BRCA1")
candidates.pit <- vsd.pit %>% dplyr::filter(genes %in% candidategenes)
candidates.pit <- as.data.frame(candidates.pit)
row.names(candidates.pit) <- candidates.pit$genes
candidates.pit$genes <- NULL
candidates.pit <- as.data.frame(t(candidates.pit))
candidates.pit$V1 <- row.names(candidates.pit) 
candidates.pit <- left_join(colData.pit, candidates.pit) 
candidates.pit$treatment <- factor(candidates.pit$treatment, levels = alllevels)
candidates.pit$study2 <- ifelse(candidates.pit$treatment %in% charlevels, "charcterization",
                              ifelse(candidates.pit$treatment %in% levelstiming, "timing",
                                     ifelse(candidates.pit$treatment %in% levelsremoval, "removal", NA)))
tail(candidates.pit)

@@

```{r}
meanBrcaPrl <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment, sex) %>%
  dplyr::summarise(meanBRCA1 = mean(BRCA1), 
                   meanPRL = mean(PRL)) %>%
  dplyr::mutate(meanBRCA1 = round(meanBRCA1,2)) %>%
  dplyr::mutate(meanPRL = round(meanPRL,1)) %>%
  dplyr::filter(treatment %in% charlevels) %>%
  droplevels() %>%
  dplyr::mutate(timepoint = as.numeric(treatment)) %>%
  select(timepoint, treatment, sex, meanPRL, meanBRCA1)
meanBrcaPrl
summary(meanBrcaPrl)
```

```{r}
write.csv(candidates.pit, "../results/16_pitPRL.csv")
write.csv(aov_all, "../results/16_aov_PRLsex.csv")
write.csv(aov_manip, "../results/16_aov_PRLsextreatment.csv")
write.csv(meanBrcaPrl, "../results/16_meanBrcaPrl.csv", row.names = F)

@@

>>>>

candidategenes <- c("PRL", "BRCA1", "PRLR")
candidates.pit <- vsd.pit %>% dplyr::filter(genes %in% candidategenes)
candidates.pit <- as.data.frame(candidates.pit)
row.names(candidates.pit) <- candidates.pit$genes
candidates.pit$genes <- NULL
candidates.pit <- as.data.frame(t(candidates.pit))
candidates.pit$V1 <- row.names(candidates.pit) 
candidates.pit <- left_join(colData.pit, candidates.pit) 
candidates.pit$treatment <- factor(candidates.pit$treatment, levels = alllevels)
candidates.pit$study2 <- ifelse(candidates.pit$treatment %in% charlevels, "charcterization",
                              ifelse(candidates.pit$treatment %in% levelstiming, "timing",
                                     ifelse(candidates.pit$treatment %in% levelsremoval, "removal", NA)))
tail(candidates.pit)

@@

```{r}
meanPRLPRLR <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment, sex) %>%
  dplyr::summarise(meanPRLR = mean(PRLR), 
                   meanPRL = mean(PRL)) %>%
  dplyr::mutate(meanPRLR = round(meanPRLR,2)) %>%
  dplyr::mutate(meanPRL = round(meanPRL,1)) %>%
  dplyr::filter(treatment %in% charlevels) %>%
  droplevels() %>%
  dplyr::mutate(timepoint = as.numeric(treatment)) %>%
  select(timepoint, treatment, sex, meanPRL, meanPRLR)
meanPRLPRLR

@@

```{r}
write.csv(candidates.pit, "../results/16_pitPRL.csv")
write.csv(aov_all, "../results/16_aov_PRLsex.csv")
write.csv(aov_manip, "../results/16_aov_PRLsextreatment.csv")
write.csv(meanPRLPRLR, "../results/16_meanPRLPRLR.csv", row.names = F)
